---
title: "Users"
output: 
    html_document:
      theme: readable
      css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align="center",
                      message = FALSE, warning = FALSE)
```

Users data in a nutshell.


### **Stack Overflow encompasses users from all over the world.**

```{r out.width="80%", message=FALSE, warning=FALSE}
plot_geo(locations, sizes = c(1, 500)) %>%
    add_markers(
        x = ~lon, y = ~lat, size = ~n, color = ~n, hoverinfo = "text",
        text = ~paste(locations$Location)
    ) %>%
    layout(title = 'User Locations', geo = g)

```


### **The majority of Stack Overflow users are males.** :

```{r fig.align='center', out.width="60%"}
ggplot(genders, aes(x = factor(1), fill = factor(gender))) +
    geom_bar(width = 1) +
    coord_polar(theta = "y") +
    labs(x = "", y = "", title = "Gender Distribution") +
    scale_fill_manual(name = "Gender", values=c("brown3", "slateblue")) +
    theme_bw() +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank())
```



### **Word Cloud of Users' AboutMe Sections** 
Users speak about their inclination and enthusiasm towards technology in their profiles !
A big number of them are programmers :)
```{r fig.align='center', out.width="110%"}
dfm_aboutme <- users$TidyAboutMe %>%
    quanteda::tokens() %>%
    dfm() %>%
    dfm_trim(min_termfreq = 10, verbose = FALSE)
# plot a wordcloud
set.seed(100)
textplot_wordcloud(dfm_aboutme, max_words = 200, rotation = 0.25,
                   color = c('blue', 'green', 'purple'))
```

This forum encompasses users of various domains. This is visualization of  "About me" section from the users profiles, to obtain most prominent words using a word cloud. This helps see what areas and skills are dominant based on the users who have provided the details.


